### 2021-05-04 content/80.formal-definition.tex
fixing more DOIs and markdown

The `Root(r)` is a type of Dataset(r), and must have the metadata to literal attributes to provide a name, description and datePublished, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 [requirements for the root data entity](https://www.researchobject.org/ro-crate/1.1/root-data-entity.html#direct-properties-of-the-root-data-entity).

The concept of an `Entity(e)` is introduced as being either a DataEntity(e), a ContextualEntity(e), or [both](https://www.researchobject.org/ro-crate/1.1/contextual-entities.html#contextual-vs-data-entities); and must be typed with at least one Class(e).

For simplicity in this formalization (and to assist production rules below) R is a constant representing a single RO-Crate, typically written to independent RO-Crate Metadata files. R is used by Mentions(R, e) to indicate that e is an Entity described by the RO-Crate and therefore its metadata (a set of Relation and Attribute predicates) form part of the RO-Crate serialization. Relation(s, p, o) and Attribute(s, p, x) are defined as a _subject-predicate-object_ triple pattern from an Entity(s) using a Property(p) to either another Entity(o) or a Literal(x) value.

@@

    RO-Crate(<http://example.com/ro/123/>)
    name(<http://example.com/ro/123/, 
        “Data files associated with the manuscript:Effects of facilitated family case …”)
    description(<http://example.com/ro/123/, 
        “Palliative care planning for nursing home residents with advanced dementia …")
    datePublished(<http://example.com/ro/123/>, “2017")
    license(<http://example.com/ro/123/>, <https://creativecommons.org/licenses/by-nc-sa/3.0/au/>
    ContextualEntity(<https://creativecommons.org/licenses/by-nc-sa/3.0/au/>)
    name(<https://creativecommons.org/licenses/by-nc-sa/3.0/au/, 
        “Attribution-NonCommercial-ShareAlike 3.0 Australia (CC BY-NC-SA 3.0 AU)”)

@@

Note that in the JSON-LD serialization of RO-Crate the expression of Class and Property is typically indirect, as the JSON-LD `@context` maps to schema.org IRIs, which when resolved as Linked Data embeds their formal definition as RDFa.

>>>>

The `Root(r)` is a type of Dataset(r), and must have the metadata to literal attributes to provide a `name`, `description` and `datePublished`, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 [requirements for the root data entity](https://www.researchobject.org/ro-crate/1.1/root-data-entity.html#direct-properties-of-the-root-data-entity).

The concept of an `Entity(e)` is introduced as being either a DataEntity(e), a `ContextualEntity(e)`, or [both](https://www.researchobject.org/ro-crate/1.1/contextual-entities.html#contextual-vs-data-entities); and must be typed with at least one `Class(e)`.

For simplicity in this formalization (and to assist production rules below) `R` is a constant representing a single RO-Crate, typically written to independent RO-Crate Metadata files. `R` is used by `Mentions(R, e)` to indicate that `e` is an Entity described by the RO-Crate and therefore its metadata (a set of Relation and Attribute predicates) form part of the RO-Crate serialization. `Relation(s, p, o)` and `Attribute(s, p, x)` are defined as a _subject-predicate-object_ triple pattern from an `Entity(s)` using a `Property(p)` to either another `Entity(o)` or a `Literal(x)` value.

@@

    RO-Crate(<http://example.com/ro/123/>)
    name(<http://example.com/ro/123/, 
        “Data files associated with the manuscript:Effects of …”)
    description(<http://example.com/ro/123/, 
        “Palliative care planning for nursing home residents …")
    datePublished(<http://example.com/ro/123/>, “2017")
    license(<http://example.com/ro/123/>, 
        <https://creativecommons.org/licenses/by-nc-sa/3.0/au/>
    ContextualEntity(<https://creativecommons.org/licenses/by-nc-sa/3.0/au/>)
    name(<https://creativecommons.org/licenses/by-nc-sa/3.0/au/, 
        “Attribution-NonCommercial-ShareAlike 3.0 Australia (CC BY-NC-SA 3.0 AU)”)

@@

Note that in the JSON-LD serialization of RO-Crate the expression of `Class` and `Property `is typically indirect, as the JSON-LD `@context` maps to schema.org IRIs, which when resolved as Linked Data embeds their formal definition as RDFa.
